Scottish Child Poverty Briefing Plots

### 2024-10-09 minos/outcomes/ChildPovReduction_plots.Rmd

@@

synthpop_uncertainty <- function(summary_group, scen, var) {
  # summary_group <- 'whole_pop'
  # scen.list <- 'baseline'  # , 'ChildPovertyReductionRELATIVE_2'

@@

>>>>

  data <- do.call(rbind, generate_df_list(summary_group, scen))

@@

SF12_change_income_quint <- function(summary_group, scen.list) {

@@

```{r}
SF12_change_income_quint2 <- function(summary_group, scen) {

  summary_group <- paste0(summary_group, '_income_quint_together')
  scen <- paste0(scen, '_together')

  data <- do.call(rbind, generate_df_list(summary_group, scen))

  plot_data <- data %>%
    select(run_id, SF_12, income_quintile, year, scenario) %>%
    pivot_wider(names_from = scenario,
                values_from = SF_12,
                names_sep = '.') %>%
    mutate(diff_SF12 = intervention - baseline) %>%
    pivot_longer(cols = starts_with("diff"),
                 names_to = c(".value", "scenario"),
                 names_sep = "\\.") %>%
    select(run_id, income_quintile, year, diff_SF12)

  plot_data_confint <- plot_data %>%
      group_by(year, income_quintile) %>%
      summarise(n = n(),
                mean_SF12_change = mean(diff_SF12),
                margin_SF12 = qt(0.975, df = n - 1) * (sd(diff_SF12) / sqrt(n)),
                lower_SF12 = mean_SF12_change - margin_SF12,
                upper_SF12 = mean_SF12_change + margin_SF12)

  plot_data_confint$income_quintile <- factor(plot_data_confint$income_quintile)

  # p1 <- ggplot(plot_data, aes(x = year, y = diff_SF_12)) +
  #     geom_hline(yintercept = 0, linetype = 'dashed') +
  #     geom_vline(xintercept = 2030, linetype = 'dotted') +
  #     geom_smooth() +
  #     labs(title = 'Treatment on the Treated',
  #          subtitle = 'SF_12') +
  #     xlab('Year') +
  #     ylab('Change in mean SF-12')

  p2 <- ggplot(plot_data_confint, aes(x = year, y = mean_SF12_change, group = income_quintile, color = income_quintile, fill = income_quintile)) +
      geom_ribbon(aes(ymin = lower_SF12, ymax = upper_SF12), linetype = 'dotted', alpha = 0.3) +
      geom_line(linetype = 'dashed') +
      geom_point() +
      geom_hline(yintercept = 0, linetype = 'dashed') +
      geom_vline(xintercept = 2030, linetype = 'dotted', alpha = 0.5) +
      labs(title = 'Treatment on the Treated',
           subtitle = 'SF_12') +
      xlab('Year') +
      ylab('Change in mean SF-12')

  #print(p1)
  print(p2)
}
```
